Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 egpaper_final.tex
Experiment section, intro minor modifications

More recently, \cite{Aubry14, Lim14} made progress in joint instance-level object detection and pose estimation. To estimate pose they use synthetic renderings of CAD models to learn discriminative mid-level patches. \cite{Aubry14} calibrates these patches on a small set of real images, while \cite{Lim14} present a method for learning the relative discriminativeness of the patches.

@@

\begin{table*}[!htbp]
    \begin{center}
\begin{tabular}{|c|c|r|c|r|}
\hline
Methods (AP/MPPE) & before calibration  & time & after Calibration \cite{Aubry14} & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.3 / 65.0  &  31ms  & 60.4 / 50.2                 &   8.7 sec \\ 
WHO\cite{Hariharan12} &              &  3811ms&                             &   12.4 sec  \\
WHO-CG                & 81.7 / \texbf{84.9}  &  104ms &     83.7 / 87.3             &   8.3 sec \\
WHO-CG-Z              & 54.4 / 65.1  &  103ms & \textbf{92.8} / 86.7 &   8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG        & \textbf{90.0} / 82.8 & 79ms & 90.3 / \textbf{86.8}                   &  8.5 sec   \\
\hline
\end{tabular}
\\\textcolor{red}{TABLE REQUIRES MODIFICATION}
\end{center}
\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method. The time column indicates the time to generate one template. We followed calibration procedure presented in \cite{Aubry14}.}
\label{tab:who_initializations}
\end{table*}

@@

Then, we show that our method can complement the detection bounding boxes coming out of standard object detectors. This process will enrich object detection bounding boxes with 2D-3D matching which gives continuous viewpoint estimation, a CAD model (rendering, depth) and fine-grained category.

\subsection{2D-3D Matching as an Object Detector} 
We created ensemble of NZ-WHO templates using 9 CAD models and measured the Average Precision (AP) of object detection task and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11}. MPPE is the average of viewpoint accuracy.

Our ensemble of NZ-WHO templates are generated from rendering image with no calibration but shows strong performance on object detection. The method we are comparing against are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}. Each method requires complex 3D modeling and viewpoint annotated natural images.
\begin{figure}[h]
    \begin{center}
    \setlength\tabcolsep{0pt}
\begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_3dobject/7.png} &   
  \includegraphics[width=0.45\linewidth]{car_3dobject/8.png}\\ [-15pt]
%   (a) & (b) \\[0pt]
  \includegraphics[width=0.45\linewidth]{car_3dobject/11.png} &   
  \includegraphics[width=0.45\linewidth]{car_3dobject/12.png}\\ [-5pt]
%  (c) & (d) \\[0pt]
\end{tabular}
\end{center}
\caption{Detection results on 3D-Object dataset \cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
  \label{fig:3dobject}
\end{figure}

% Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image. Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs. Similarly, \cite{Lim14}
\begin{table}[!htbp]
  \begin{center}
    \begin{tabular}{|c|c|c|c|}
    \hline
     AP/MPPE& Ours & ALM\cite{Xiang12} & VOCDPM\cite{Pepik12} \\
    \hline\hline
    car & \textbf{99.8}/91.7 &  98.4/93.4 & \textbf{99.8}/\textbf{97.5} \\ 
    bicycle & 93.0/87.4 & 93.0/91.4 & \textbf{98.8}/\textbf{97.5} \\
    \hline
    \end{tabular}
  \end{center}
  \caption{Average Precision(AP) and Average Viewpoint Accuracy(AVA) on 3DObject dataset. Though we do not need any training images and made templates in few minues, it performs on par with state of the art detectors yet it gives high quality 2D-3D matching.}
  \label{tab:3dobject}
\end{table}

@@

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|c|c|c|}
   \hline
  \includegraphics[width=0.24\textwidth]{car_cnn/1a.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/1b.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/1c.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/1d.png}  \\  
   \hline
  \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/2b.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/2c.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  
   \hline
  \includegraphics[width=0.24\textwidth]{car_cnn/4a.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/4b.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/4c.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/4d.png}  \\  
%    \hline
%   \includegraphics[width=0.24\textwidth]{car_cnn/10a.png} &   
%   \includegraphics[width=0.24\textwidth]{car_cnn/10b.png} &   
%   \includegraphics[width=0.24\textwidth]{car_cnn/10c.png} &   
%   \includegraphics[width=0.24\textwidth]{car_cnn/10d.png}  \\  
%   \hline 
%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3a.png} &   
%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3b.png} &   
%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3c.png} &   
%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3d.png}  \\
  \hline
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7a.png} &   
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7b.png} &   
  &\\
  \hline
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4a.png} &   
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4b.png} &   
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4c.png} &   
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4d.png}  \\
  \hline
  CNN Proposals & \multicolumn{3}{|c|}{Our matching results on proposal bounding boxes} \\
  \hline
\end{tabular}
\caption{Example enriched bounding boxex. Given R-CNN\cite{Girshick14} detection bounding boxes, our method predicted 2D-3D matching reasonably. On the first column, R-CNN detection bounding boxes overlaid. From the second to the last columns, output of our method given a R-CNN box. Blue boxes are R-CNN output and purle boxes are the tightest bounding box enclosing predicted CAD model}
  \label{fig:pascal12cnn}
\end{figure*}

\begin{table*}[!htbp]
    \footnotesize
  \begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
AP/AVP              & VDPM \cite{Xiang14} & VOC-DPM \cite{Pepik12}  & \cite{Pepik12} + Ours (discrete) & \cite{Pepik12} + Ours (full) & R-CNN + Ours (discrete) & R-CNN + Ours (full)\\
\hline\hline
car-4v              & 37.2 / 20.2         & 45.6 / 36.9             & 47.6 / 42.7       & 47.6 / \textbf{42.7}        & 49.6 / 41.5         & 49.6 / 41.5\\ \hline
car-8v              & 37.3 / 23.5         & 47.6 / 36.6             & 47.6 / \textbf{39.8}       & 47.6 / 39.5        & 49.6 / 38.0         & 49.6 / 39.0\\ \hline
car-16v             & 36.6 / 18.1         & 46.0 / 29.6             & 47.6 / 32.7       & 47.6 / 33.0        & 49.6 / 34.0         & 49.6 / \textbf{34.3}\\ \hline
car-24v             & 36.3 / 13.7         & 42.1 / 24.6             & 47.6 / 27.4       & 47.6 / 27.4        & 49.6 / 27.0         & 49.6 / \textbf{27.6}\\ \hline
\hline
bicycle-4v          & 45.2 / 41.7         & 46.9 / 43.9             & 48.1 / 47.6       & 48.1 / 46.6        & 61.7 / 56.5         & 61.7 / \textbf{56.7}\\ \hline
bicycle-8v          & 47.3 / 36.7         & 48.1 / 40.3             & 48.1 / 40.6       & 48.1 / 40.6        & 61.7 / 48.9         & 61.7 / \textbf{49.2}\\ \hline
bicycle-16v         & 46.5 / 18.4         & 45.6 / 22.9             & 48.1 / 26.2       & 40.1 / 27.3        & 61.7 / 34.7         & 61.7 / \textbf{35.8}\\ \hline
bicycle-24v         & 44.4 / 14.3         & 45.9 / 16.7             & 48.1 / 21.5       & 40.1 / 20.9        & 61.7 / \textbf{27.0}         & 61.7 / 23.9\\ \hline
\end{tabular}
\end{center}
\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) on PASCAL 3D dataset\cite{Xiang14}. For combined method (* + Ours), we use bounding boxes from * and augment viewpoint using our method. R-CNN and run our method to produce 2D-3D matching. If our method fails to give viewpoint, it predicts the viewpoint to be 0. Note that our method gives high quality metadata such as continuous 3D viewpoint, CAD model (rendering depth) and fine-grained category, whereas base-line methods gives 1D discrete azimuths. Our R-CNN was not an optimized version so the detection AP is lower than the state-of-the-art R-CNN performance}
\label{tab:pascal12}
\end{table*}

@@

Generic object detectors sometimes give overlapping detection bounding boxes of the same object with different aspect ratio or truncation. For instance, R-CNN \cite{Girshick14} usually gives very irregular bounding boxes since the proposals bounding boxes comes from various methods.

To handle such irregular shape and truncation, we added small context around the bounding boxes and run our method. We consider all possible truncation which can be efficiently computed using FFT-based convolution (refer Section. \ref{sec:fft}). We put examples of such conditions in Figure \ref{fig:stability}. Although the input bounding boxex are drastically different and have sever truncations. Our method reliably generated reasonable prediction of pose and model.

>>>>

More recently, \cite{Aubry14, Lim14} made progress in joint instance-level object detection and pose estimation. To estimate pose they use synthetic renderings of CAD models to learn discriminative mid-level patches. \cite{Aubry14} calibrates these patches on a small set of real images, while \cite{Lim14} presents a method for learning the relative discriminativeness of the patches.

@@

\begin{table*}[!htbp]
    \begin{center}
\begin{tabular}{|c|c|r|c|r|}
\hline
Methods (AP/MPPE) & before calibration  & time & after Calibration \cite{Aubry14} & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.3 / 65.0  &  31ms  & 60.4 / 50.2                 &   8.7 sec \\ 
WHO\cite{Hariharan12} & 82.1 / 85.4  &  3811ms&                             &   12.4 sec  \\
WHO-CG                & 81.7 / \textbf{84.9}  &  104ms &     83.7 / 87.3             &   8.3 sec \\
WHO-CG-Z              & 54.4 / 65.1  &  103ms & \textbf{92.8} / 86.7 &   8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG        & \textbf{90.0} / 82.8 & 79ms & 90.3 / \textbf{86.8}                   &  8.5 sec   \\
\hline
\end{tabular}
\\\textcolor{red}{TABLE REQUIRES MODIFICATION}
\end{center}
\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method. The time column indicates the time to generate one template. We followed calibration procedure presented in \cite{Aubry14}.}
\label{tab:who_initializations}
\end{table*}

@@

Second, we show that our method can complement the detection bounding boxes coming out of standard object detectors. This process will enrich object detection bounding boxes with 2D-3D matching which gives continuous viewpoint estimation, a CAD model (rendering, depth) and fine-grained category.

\subsection{2D-3D Matching as an Object Detector}

We created ensemble of NZ-WHO templates using 9 CAD models and measured the Average Precision (AP) of object detection task and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11}. MPPE is the average of viewpoint accuracy.

Our ensemble of NZ-WHO templates is generated from rendering image with no calibration but shows strong performance on object detection. The baseline method are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}. Note that the baseline methods require complex 3D modeling and viewpoint annotated natural images.

The detection result is on Table \ref{tab:3dobject} and example output from our method is on Figure \ref{fig:3dobject}.

\begin{figure}[h]
    \begin{center}
    \setlength\tabcolsep{0pt}
\begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_3dobject/7.png} &   
  \includegraphics[width=0.45\linewidth]{car_3dobject/8.png}\\ [-15pt]
%   (a) & (b) \\[0pt]
  \includegraphics[width=0.45\linewidth]{car_3dobject/11.png} &   
  \includegraphics[width=0.45\linewidth]{car_3dobject/12.png}\\ [-5pt]
%  (c) & (d) \\[0pt]
\end{tabular}
\end{center}
\caption{Detection results on 3D-Object dataset \cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
  \label{fig:3dobject}
\end{figure}

% Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image. Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs. Similarly, \cite{Lim14}
\begin{table}[!htbp]
  \begin{center}
    \begin{tabular}{|c|c|c|c|}
    \hline
     AP/MPPE& Ours & ALM\cite{Xiang12} & VOCDPM\cite{Pepik12} \\
    \hline\hline
    car & \textbf{99.8}/91.7 &  98.4/93.4 & \textbf{99.8}/\textbf{97.5} \\ 
    bicycle & 93.0/87.4 & 93.0/91.4 & \textbf{98.8}/\textbf{97.5} \\
    \hline
    \end{tabular}
  \end{center}
  \caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) on 3DObject dataset car category. Our method produces high quality 2D-3D matching yet performs on par with state-of-the art detectors.}
  \label{tab:3dobject}
\end{table}

@@

We used detection bounding boxes and augment it using our method to give viewpoint estimation. We used detection bounding boxes from two different methods: VOC-DPM \cite{Pepik12} and R-CNN \cite{Girshick14}. VOC-DPM is a variation of DPM that can estimate viewpoint and is the state-of-the-art performance in viewpoint estimation \cite{Xiang14}. The result is on Table \ref{tab:pascal12} and precision recall curves for car using R-CNN + Ours are on Figure \ref{fig:car_cnn_ap}.

We got significant improvement on viewpoint estimation by using our method on top of general purpose detectors. Note that our method estimates azimuth, elevation, in-plane rotation, focal length estimation, fine-grained categorization whereas V-DPM, VOC-DPM only estimate discrete viewpoints.

Example outputs are on Figure \ref{fig:pascal12cnn}.

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|c|c|c|}
   \hline
  \includegraphics[width=0.24\textwidth]{car_cnn/1a.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/1b.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/1c.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/1d.png}  \\  
   \hline
  \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/2b.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/2c.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  
   \hline
  \includegraphics[width=0.24\textwidth]{car_cnn/4a.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/4b.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/4c.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/4d.png}  \\  
%    \hline
%   \includegraphics[width=0.24\textwidth]{car_cnn/10a.png} &   
%   \includegraphics[width=0.24\textwidth]{car_cnn/10b.png} &   
%   \includegraphics[width=0.24\textwidth]{car_cnn/10c.png} &   
%   \includegraphics[width=0.24\textwidth]{car_cnn/10d.png}  \\  
%   \hline 
%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3a.png} &   
%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3b.png} &   
%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3c.png} &   
%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3d.png}  \\
  \hline
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7a.png} &   
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7b.png} &   
  &\\
  \hline
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4a.png} &   
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4b.png} &   
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4c.png} &   
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4d.png}  \\
  \hline
  CNN Proposals & \multicolumn{3}{|c|}{Our matching results on proposal bounding boxes} \\
  \hline
\end{tabular}
\caption{Example enriched bounding boxes. Given R-CNN\cite{Girshick14} detection bounding boxes, our method predicted 2D-3D matching reasonably. On the first column, R-CNN detection bounding boxes overlaid. From the second to the last columns, output of our method given a R-CNN box. Blue boxes are R-CNN output and purple boxes are the tightest bounding box enclosing predicted CAD model}
  \label{fig:pascal12cnn}
\end{figure*}

\begin{table*}[!htbp]
    \footnotesize
  \begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
AP/AVP              & V-DPM \cite{Xiang14} & VOC-DPM \cite{Pepik12}  & \cite{Pepik12} + Ours (discrete) & \cite{Pepik12} + Ours (full) & R-CNN + Ours (discrete) & R-CNN + Ours (full)\\
\hline\hline
car-4v              & 37.2 / 20.2         & 45.6 / 36.9             & 47.6 / 42.7       & 47.6 / \textbf{42.7}        & 49.6 / 41.5         & 49.6 / 41.5\\ \hline
car-8v              & 37.3 / 23.5         & 47.6 / 36.6             & 47.6 / \textbf{39.8}       & 47.6 / 39.5        & 49.6 / 38.0         & 49.6 / 39.0\\ \hline
car-16v             & 36.6 / 18.1         & 46.0 / 29.6             & 47.6 / 32.7       & 47.6 / 33.0        & 49.6 / 34.0         & 49.6 / \textbf{34.3}\\ \hline
car-24v             & 36.3 / 13.7         & 42.1 / 24.6             & 47.6 / 27.4       & 47.6 / 27.4        & 49.6 / 27.0         & 49.6 / \textbf{27.6}\\ \hline
\hline
bicycle-4v          & 45.2 / 41.7         & 46.9 / 43.9             & 48.1 / 47.6       & 48.1 / 46.6        & 61.7 / 56.5         & 61.7 / \textbf{56.7}\\ \hline
bicycle-8v          & 47.3 / 36.7         & 48.1 / 40.3             & 48.1 / 40.6       & 48.1 / 40.6        & 61.7 / 48.9         & 61.7 / \textbf{49.2}\\ \hline
bicycle-16v         & 46.5 / 18.4         & 45.6 / 22.9             & 48.1 / 26.2       & 40.1 / 27.3        & 61.7 / 34.7         & 61.7 / \textbf{35.8}\\ \hline
bicycle-24v         & 44.4 / 14.3         & 45.9 / 16.7             & 48.1 / 21.5       & 40.1 / 20.9        & 61.7 / \textbf{27.0}         & 61.7 / 23.9\\ \hline
\end{tabular}
\end{center}
\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) on PASCAL 3D dataset\cite{Xiang14}. For combined method (* + Ours), we use bounding boxes from * and augment viewpoint using our method. R-CNN and run our method to produce 2D-3D matching. If our method fails to give viewpoint, it predicts the viewpoint to be 0. Note that our method gives high quality metadata such as continuous 3D viewpoint, CAD model (rendering depth) and fine-grained category, whereas base-line methods gives 1D discrete azimuths. Our R-CNN was not an optimized version so the detection AP is lower than the state-of-the-art R-CNN performance}
\label{tab:pascal12}
\end{table*}

\begin{figure}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{cc}
  \hline
  \includegraphics[width=0.49\linewidth]{car_cnn4_crop.png} &   
  \includegraphics[width=0.49\linewidth]{car_cnn8_crop.png} \\   
  \includegraphics[width=0.49\linewidth]{car_cnn16_crop.png} &   
  \includegraphics[width=0.49\linewidth]{car_cnn24_crop.png} \\   
  \hline
\end{tabular}
\caption{Average Precision (AP) and Average Viewpoint Precision (AVP) and viewpoint confusion table on PASCAL 12 car validation set using R-CNN + Ours. From the top left, 4 views, 8 views, 16 views and 24 views. Since our method only augment the object detection, the AP remains the same for all cases. As we increase the viewpoint estimation, the AVP decreases. Note that since we estimate null viewpoint if our method fails to find match, there are more 0 viewpoint predictions (top row of confusion matrices) }
  \label{fig:car_cnn_ap}
\end{figure}

@@

% Generic object detectors give overlapping detection bounding boxes of the same object which can be handled by non maximal suppression. For these overlapping detections,

R-CNN detection bounding boxes are irregular in shape since they come from other region proposal methods and sometimes they truncate objects. To handle such irregular shape and truncation, we added small context around the bounding boxes and run our method.

We assumed that object can be arbitrarily truncated by the bounding box and search all plausible scales and translations. This can be efficiently computed using FFT-based convolution (refer Section. \ref{sec:fft}). We put examples of such conditions in Figure \ref{fig:stability}. Although the input bounding boxes are irregular and truncate objects, our method reliably generated a reasonable prediction of pose, translation, scale and CAD model.

% R-CNN \cite{Girshick14} gives very irregular bounding boxes since the proposals bounding boxes come from various methods.

### 2014-11-14 intro.tex
Experiment section, intro minor modifications

In this paper, we propose a novel method for 2D-3D alignment of
exemplar CAD models to real-world images that circumvents the need for
calibration, and greatly enhances the scalability of E-LDA. As a
result, we can render novel views and train corresponding exemplar
models {\em on the fly}, without the need for offline processing. As a
by-product, we can formulate the alignment problem as a parameter
search in a continuos pose space, consisting of yaw, pitch and roll, resulting in truely continuous pose estimates, which
we implement using MCMC sampling.
%  require a large number of rendering and 2D
% templates for each of the CAD model with specific viewpoint. Since
% there are so many templates that it becomes almost impossible to get
% all the true positive image from training data. Instead \cite{Aubry14,
%   Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to
% make templates more discriminative. Then calibration is done on a
% small training dataset.
%
% Although whitening to create template is faster than some of
% instance-level matching algorithms such as training Exemplar-SVM
% \cite{Malisiewicz11} or complicated models such as LEVAN
% \cite{Divvala14}, whitening and calibration large number of templates
% takes very long time. Also, once the fixed discrete viewpoint
% templates have been made and calibrated, it is difficult to fine-tune
% the prediction made using the large collection of templates.

@@

First, we present a novel method for training exemplar models from
rendered 3D CAD data {\em on the fly}, enabled by a novel variant of
E-LDA, and making efficient use of the specific characteristics of
rendered images. To our knowledge, our method constitutes the first
attempt to simultanously render and train exemplar detectors on the
fly.
% In our paper, we present Non-Zero Whiten Histograms of Orientations
% (NZ-WHO) to dramatically speed up the template generation and get rid
% of time consuming calibration and yet achieves performance on par with
% calibrated templates. First, we will present NZ-WHO is more
% discriminative than WHO and introduce Conjugate Gradient method to
% speed up the whitening and create a high resolution template in just
% 80 milliseconds. Also, using this fast NZ-WHO template generation, we
% present \textbf{on-the-fly} template generation to fine tune an
% initial pose estimation to continuously refine translation, viewpoints
% (yaw, roll, pitch) and focal length.

Second, we show to enrich the output of an existing object class
detector, such as the DPM~\cite{Felzenszwalb10} or the
R-CNN~\cite{Girshick14} with additional 3D information, applying our
method to candidate detections provided by the respective detector. As
a result, we can refine the original detections with additional
estimates of 3D continuos pose and a 3D CAD model exemplar.

@@

Our pipeline is simple, fast only requires CAD models and no
validation images for calibration. This can be used for post
processing stage of generic object detection. Our pipeline requires
only several minutes to make templates for rough viewpoints and

@@

Finally, we show several applications using our method. Since we have
metadata such as CAD model and geometry, we reconstruct the object
using 2D-3D matching. Also, since we do not need training image, we
show that our 2D-3D matching performs better than standard detectors
in categories where training data lacks. We then use our method for
image query to pull out closest CAD model in a bank of CAD models.

Finally, unlike several CAD model alignment methods that uses  WHO
\cite{Aubry13, Aubry14, Lim14}, we propose a novel pipeline that does
not require calibration which is infeasible in continuous viewpoint
estimation. We propose a simple add-on stage that can enrich object
detections with high-quality 2D-3D alignment. The pipeline is simple
and light weight so this can be easily adapted to be used for any
generic object detectors. Also to facilitate the future work, all our
alignment result on PASCAL12 and code are publicly available online.

@@

\subsection{Approach Overview}
Our method is in line with \cite{Aubry14, Lim14} in the sense that we
use only renderings not real images. However, rather than using fixed
sized mid-level patches, we use whole object and make root
templates. By using root templates, there is no need to learn a
discriminative patch dictionary or to calibrate the patches and an
additional inference stage is not required. However, whitening the
whole template is prohibitive for several reasons. All templates have
different aspect ratios making it difficult to generate the covariance
matrix $\Sigma$. Since the root templates are larger than mid-level
patches, a very large auto-covariance $\Gamma$ is required. Lastly,
time complexity of decorrelating a template with $n$ cells increases
as $O(n^3)$, resulting in slow template generation and large residuals
due to numerical errors accumulated while decomposing the covariance
matrix $\Sigma$.

To overcome these difficulties, we propose the Non-Zero Whitened
Histograms of Orientations with iterative Conjugate Gradient to
generate templates in real time and enrich rectangular boxes with high
quality 2D-3D matching. The 2D-3D matching provides a CAD model,
sub-category, rendering, depth, viewpoint and focal length.

Our method can work as a standalone 2D-3D matching algorithm, or even
as a standalone ensemble of exemplar-based object detectors (Figure
\ref{fig:front}) but the real power comes from combining generic
object detectors and complement rectangular bounding boxes. Our method
is simple in design; is several orders of magnitude faster than
traditional method; requires only CAD models; doesn't need images nor
calibration, yet is powerful in giving high-quality metadata. These
properties make our method ideal for complementing object detections.

>>>>

In this paper, we propose a novel method for 2D-3D alignment of
exemplar CAD models to real-world images that circumvents the need for
calibration, and greatly enhances the scalability of E-LDA. As a
result, we can render novel views and train corresponding exemplar
models {\em on the fly}, without the need for offline processing. As a
by-product, we can formulate the alignment problem as a parameter
search in a continuous pose space, consisting of yaw, pitch and roll, resulting in truely continuous pose estimates, which
we implement using MCMC sampling.
%  require a large number of rendering and 2D
% templates for each of the CAD model with specific viewpoint. Since
% there are so many templates that it becomes almost impossible to get
% all the true positive image from training data. Instead \cite{Aubry14,
%   Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to
% make templates more discriminative. Then calibration is done on a
% small training dataset.
%
% Although whitening to create template is faster than some of
% instance-level matching algorithms such as training Exemplar-SVM
% \cite{Malisiewicz11} or complicated models such as LEVAN
% \cite{Divvala14}, whitening and calibration large number of templates
% takes very long time. Also, once the fixed discrete viewpoint
% templates have been made and calibrated, it is difficult to fine-tune
% the prediction made using the large collection of templates.

@@

First, we present a novel method for training exemplar models from
rendered 3D CAD data {\em on the fly}, enabled by a novel variant of
E-LDA, and making efficient use of the specific characteristics of
rendered images. To our knowledge, our method constitutes the first
attempt to simultaneously render and train exemplar detectors on the
fly.
% In our paper, we present Non-Zero Whiten Histograms of Orientations
% (NZ-WHO) to dramatically speed up the template generation and get rid
% of time consuming calibration and yet achieves performance on par with
% calibrated templates. First, we will present NZ-WHO is more
% discriminative than WHO and introduce Conjugate Gradient method to
% speed up the whitening and create a high resolution template in just
% 80 milliseconds. Also, using this fast NZ-WHO template generation, we
% present \textbf{on-the-fly} template generation to fine tune an
% initial pose estimation to continuously refine translation, viewpoints
% (yaw, roll, pitch) and focal length.

Second, we show to enrich the output of an existing object class
detector, such as the DPM~\cite{Felzenszwalb10} or the
R-CNN~\cite{Girshick14} with additional 3D information, applying our
method to candidate detections provided by the respective detector. As
a result, we can refine the original detections with additional
estimates of 3D continuous pose and a 3D CAD model exemplar.

@@

Our pipeline is simple, fast only requires CAD models and no
validation images for calibration. This can be used for post
processing stage of generic object detection. Our pipeline requires
only few minutes to make templates for rough viewpoints and

@@

Finally, we show several applications using our method. Since we have
metadata such as CAD model and geometry, we reconstruct the object
using 2D-3D matching. Also, since we do not need training image, we
show that our 2D-3D matching performs better than standard detectors
in categories where training data is insufficient. We then use our method for
image query to pull out the closest CAD model in a bank of CAD models.

Finally, unlike several CAD model alignment methods that uses  WHO
\cite{Aubry13, Aubry14, Lim14}, we propose a novel pipeline that does
not require calibration which is infeasible in continuous viewpoint
estimation. We propose a simple add-on stage that can enrich object
detections with high-quality 2D-3D alignment. The pipeline is simple
and light weight so this can be easily adapted to be used for any
generic object detectors. Also to facilitate future work, all our
alignment result on PASCAL12 and code are publicly available online.

@@

\subsection{Approach Overview}
Our method is in line with \cite{Aubry14, Lim14} in the sense that we
use only renderings, not real images. However, rather than using fixed
sized mid-level patches, we use whole objects and make root
templates. By using root templates, there is no need to learn a
discriminative patch dictionary or to calibrate the patches and an
additional inference stage is not required. However, whitening the
whole template is prohibitive for several reasons. All templates have
different aspect ratios making it difficult to generate the covariance
matrix $\Sigma$. Since the root templates are larger than mid-level
patches, a very large auto-covariance $\Gamma$ is required. Lastly,
time complexity of decorrelating a template with $n$ cells increases
as $O(n^3)$, resulting in slow template generation and large residuals
due to numerical errors accumulated while decomposing the covariance
matrix $\Sigma$.

To overcome these difficulties, we propose the Non-Zero Whitened
Histograms of Orientations (NZ-WHO) with iterative Conjugate Gradient to
generate templates in real time and enrich rectangular boxes with high
quality 2D-3D matching. The 2D-3D matching provides a CAD model,
sub-category, rendering, depth, viewpoint and focal length.

Our method can work as a standalone 2D-3D matching algorithm, or even
as a standalone ensemble of exemplar-based object detectors (Figure
\ref{fig:front}) but its real power comes from combining generic
object detectors and complement rectangular bounding boxes. Our method
is simple in design; is several orders of magnitude faster than
traditional method; requires only CAD models; does not need neither images nor
calibration, yet is powerful in giving high-quality metadata. These
properties make our method ideal for complementing object detections.
